Examination and replication of the factorial validity and subscale reliability of the Maltreatment and Abuse Chronology of Exposure (MACE) scale

### 2022-10-24 manuscript/main.tex
fix typo
resubmission

% define title page
\title{Confirmatory factor analysis of the Maltreatment and Abuse Chronology of Exposure (MACE) scale: Evidence for essential unidimensionality}
\shorttitle{Confirmatory factor analysis of the MACE}
\author{Samuel Zorowitz$^{1*}$, Lauri Tuominen$^{2}$}
\affiliation{$^1$Princeton Neuroscience Institute, Princeton University, USA\\$^2$The Royal’s Institute of Mental Health Research, University of Ottawa, Canada}

@@

\noindent \textbf{Background}: The Maltreatment and Abuse Chronology of Exposure (MACE) scale is a retrospective self-report scale that measures 10 distinct types of childhood maltreatment. Despite its increasing use, the factor structure of the MACE has not been thoroughly investigated. As such, the viability of the MACE total and subscale scores are uncertain.

@@

\noindent \textbf{Objectives}: The current study investigated the factor structure of the MACE in order to quantify the reliability of its total and subscale scores.

@@

\noindent \textbf{Participants and setting}: Two independent samples of participants (N=1051 \& N=582) who completed the MACE were included in this study.

@@

\noindent \textbf{Methods}: Using confirmatory item response models, we tested one-factor and several bifactor models of participants' responses. We used model-based indices to estimate the reliability of the MACE total and subscale scores, and to quantify the essential unidimensionality of the scale.

\noindent \textbf{Results}: We found the MACE total score was a reliable and valid measure of overall childhood maltreatment. In contrast, although we found MACE subscale scores exhibited adequate reliability, the vast majority of their reliable variance reflected general maltreatment and not any particular type of maltreatment as intended. We also found that the MACE is essentially unidimensional and some of its items exhibit of differential item functioning by gender.

\noindent \textbf{Conclusions}: Our results provide support for a one-factor structure of the MACE, as well as continued use of the MACE total score. Our results caution against the use of MACE subscale scores, which have little practical use insofar that they provide little unique, reliable information above and beyond the total score.

>>>>

% define title page
\title{Examination and replication of the factorial validity and subscale reliability of the Maltreatment and Abuse Chronology of Exposure (MACE) scale}
\shorttitle{Factorial validity of the MACE}
\author{Samuel Zorowitz$^{1*}$, Lauri Tuominen$^{2}$}
\affiliation{$^1$Princeton Neuroscience Institute, Princeton University, USA\\$^2$The Royal’s Institute of Mental Health Research, University of Ottawa, Canada}

@@

\noindent \textbf{Objective}: The Maltreatment and Abuse Chronology of Exposure (MACE) scale is a retrospective self-report measure of childhood maltreatment. Despite increasing use, the factor structure of the MACE has not been previously investigated. As such, the psycho- metric properties of the MACE total and subscale scores are indeterminate. The aims of the current study was to examine the factorial validity of the MACE and the reliability of its total and subscale scores.

@@

\noindent \textbf{Methods}: We analyzed the response data from two independent samples of participants (N=1051 \& N=582) using confirmatory factor analysis. We fit a series of models with increasing dimensionality to explore factorial validity. Furthermore, we used model-based indices to estimate the reliability of the MACE total and subscale scores, and to test for essential unidimensionality.

@@

\noindent \textbf{Results}: Confirmatory factor analysis indicated that a bifactor S-1 model with two specific factors (peer victimization, reverse-scoring) provided the best and most parsimonious fit to the data. Despite this, model-based indices suggested the MACE scale is essentially unidimensional. We found the MACE total score was a reliable and valid measure of overall childhood maltreatment. In contrast, the MACE subscale scores exhibited little reliable variance after controlling for general maltreatment.

@@

\noindent \textbf{Conclusions}: Our results suggest the MACE is essentially unidimensional and support the continued use of the MACE total score. However, our results caution against the use of MACE subscores, which provide little unique or reliable information above and beyond the total score.
